Follow-up Samples

### 2017-09-13 submission/manuscript_R2.Rmd
fix NAs in text

All models included only OTU data obtained from 16S rRNA sequencing and were processed and cleaned using the R package caret (v`r paste(packageVersion("caret"))`). Optimization of the mtry hyper-parameter involved making 100 different 80/20 (train/test) splits of the data where the same proportion was present within both the whole data set and the 80/20 split. For each of the different splits, 20 repeated 10-fold cross validation was performed on the 80% component to optimize the mtry hyper-parameter by maximizing the AUC (Area Under the Curve of the Receiver Operator Characteristic). The resulting model was then tested on the hold out data obtained from the 20% component. For adenoma pre versus post-treatment models the optimized mtrys were `r names(table(adn_treat_AUC_summary$best_mtry))[1]` (n = `r table(adn_treat_AUC_summary$best_mtry)[1]`), `r names(table(adn_treat_AUC_summary$best_mtry))[2]` (n = `r table(adn_treat_AUC_summary$best_mtry)[2]`), and `r names(table(adn_treat_AUC_summary$best_mtry))[3]` (n = `r table(adn_treat_AUC_summary$best_mtry)[3]`) for adenoma. For advanced adenoma the mtrys were  `r names(table(srn_treat_AUC_summary$best_mtry))[1]` (n = `r table(srn_treat_AUC_summary$best_mtry)[1]`), `r names(table(srn_treat_AUC_summary$best_mtry))[2]` (n = `r table(srn_treat_AUC_summary$best_mtry)[2]`), and `r names(table(srn_treat_AUC_summary$best_mtry))[3]` (n = `r table(srn_treat_AUC_summary$best_mtry)[3]`). For carcinoma the mtrys were  `r names(table(crc_treat_AUC_summary$best_mtry))[1]` (n = `r table(crc_treat_AUC_summary$best_mtry)[1]`), `r names(table(crc_treat_AUC_summary$best_mtry))[2]` (n = `r table(crc_treat_AUC_summary$best_mtry)[2]`), and `r names(table(crc_treat_AUC_summary$best_mtry))[3]` (n = `r table(crc_treat_AUC_summary$best_mtry)[3]`). For the normal versus diagnosis models the optimized mtrys were `r names(table(adn_AUC_run_summary$best_mtry))[1]` (n = `r table(adn_AUC_run_summary$best_mtry)[1]`), `r names(table(adn_AUC_run_summary$best_mtry))[2]` (n = `r table(adn_AUC_run_summary$best_mtry)[2]`), and `r names(table(adn_AUC_run_summary$best_mtry))[3]` (n = `r table(adn_AUC_run_summary$best_mtry)[3]`) for adenoma. For advanced adenoma `r names(table(srn_AUC_run_summary$best_mtry))[1]` (n = `r table(srn_AUC_run_summary$best_mtry)[1]`), `r names(table(srn_AUC_run_summary$best_mtry))[2]` (n = `r table(srn_AUC_run_summary$best_mtry)[2]`), and `r names(table(srn_AUC_run_summary$best_mtry))[3]` (n = `r table(srn_AUC_run_summary$best_mtry)[3]`). For carcinoma `r names(table(crc_AUC_run_summary$best_mtry))[1]` (n = `r table(crc_AUC_run_summary$best_mtry)[1]`), `r names(table(crc_AUC_run_summary$best_mtry))[2]` (n = `r table(crc_AUC_run_summary$best_mtry)[2]`), and `r names(table(crc_AUC_run_summary$best_mtry))[3]` (n = `r table(crc_AUC_run_summary$best_mtry)[3]`). The hyper-parameter, mtry, defines the number of variables to investigate at each split before a new division of the data was created with the Random Forest model [@breiman_random_2001].

>>>>

All models included only OTU data obtained from 16S rRNA sequencing and were processed and cleaned using the R package caret (v`r paste(packageVersion("caret"))`). Optimization of the mtry hyper-parameter involved making 100 different 80/20 (train/test) splits of the data where the same proportion was present within both the whole data set and the 80/20 split. For each of the different splits, 20 repeated 10-fold cross validation was performed on the 80% component to optimize the mtry hyper-parameter by maximizing the AUC (Area Under the Curve of the Receiver Operator Characteristic). The resulting model was then tested on the hold out data obtained from the 20% component. For adenoma pre versus post-treatment models the optimized mtrys were `r names(table(adn_treat_AUC_summary$best_mtry))[1]` (n = `r table(adn_treat_AUC_summary$best_mtry)[1]`), `r names(table(adn_treat_AUC_summary$best_mtry))[2]` (n = `r table(adn_treat_AUC_summary$best_mtry)[2]`), and `r names(table(adn_treat_AUC_summary$best_mtry))[3]` (n = `r table(adn_treat_AUC_summary$best_mtry)[3]`) for adenoma. For advanced adenoma the mtrys were  `r names(table(srn_treat_AUC_summary$best_mtry))[1]` (n = `r table(srn_treat_AUC_summary$best_mtry)[1]`), `r names(table(srn_treat_AUC_summary$best_mtry))[2]` (n = `r table(srn_treat_AUC_summary$best_mtry)[2]`), and `r names(table(srn_treat_AUC_summary$best_mtry))[3]` (n = `r table(srn_treat_AUC_summary$best_mtry)[3]`). For carcinoma the mtrys were  `r names(table(crc_treat_AUC_summary$best_mtry))[1]` (n = `r table(crc_treat_AUC_summary$best_mtry)[1]`), `r names(table(crc_treat_AUC_summary$best_mtry))[2]` (n = `r table(crc_treat_AUC_summary$best_mtry)[2]`), and `r names(table(crc_treat_AUC_summary$best_mtry))[3]` (n = `r table(crc_treat_AUC_summary$best_mtry)[3]`). For the normal versus diagnosis models the optimized mtrys were `r names(table(adn_AUC_run_summary$mtry))[1]` (n = `r table(adn_AUC_run_summary$mtry)[1]`), `r names(table(adn_AUC_run_summary$mtry))[2]` (n = `r table(adn_AUC_run_summary$mtry)[2]`), and `r names(table(adn_AUC_run_summary$mtry))[3]` (n = `r table(adn_AUC_run_summary$mtry)[3]`) for adenoma. For advanced adenoma `r names(table(srn_AUC_run_summary$mtry))[1]` (n = `r table(srn_AUC_run_summary$mtry)[1]`), `r names(table(srn_AUC_run_summary$mtry))[2]` (n = `r table(srn_AUC_run_summary$mtry)[2]`), and `r names(table(srn_AUC_run_summary$mtry))[3]` (n = `r table(srn_AUC_run_summary$mtry)[3]`). For carcinoma `r names(table(crc_AUC_run_summary$mtry))[1]` (n = `r table(crc_AUC_run_summary$mtry)[1]`) and `r names(table(crc_AUC_run_summary$mtry))[2]` (n = `r table(crc_AUC_run_summary$mtry)[2]`). The hyper-parameter, mtry, defines the number of variables to investigate at each split before a new division of the data was created with the Random Forest model [@breiman_random_2001].
